M-Estimation of Principal Effects using Principal Scores

### 2022-06-28 writeUps/paper.tex
cleaning up displaySim.r pt 1

\subsection{Relaxing Covariate Ignorability}
In most applications, identifying a set of covariates $\bxs$ satisfying CI will be difficult or impossible.
Fortunately, CI may be relaxed or obviated by regression.
Let $\bxy\in \mathbb{R}^k$, be a vector of covariates (possibly the same as $\bxs$); $\bxy$ can contain transformations and interactions of baseline covariates, allowing for a wide range of models.
Then note that $\st$ is, essentially, a covariate, so by randomization, (Assumption \ref{ass:rand}), $\EE[\bxy|\st]=\EE[\bxy|\st,Z=0]=\EE[\bxy|\st,Z=1]$.
Then information about the stratum-specific means of $\bxy$ can be extrapolated from the treatment to the control group.
This leads to the following proposition:
\begin{prop}\label{prop:interactions}
  Say
  \begin{equation}\label{eq:interaction}
    \begin{split}
      Y_{Ci}=\beta_0^C+\bm{\beta_1}^{C'}\bxy_i+\beta_2^C\sti+\bm{\beta_3^C}'\bxy_i\sti+\epsilon_{Ci}\\
      Y_{Ti}=\beta_0^T+\bm{\beta_1}^{T'}\bxy_i+\beta_2^T\sti+\bm{\beta_3^T}'\bxy_i\sti+\epsilon_{Ti}\\
    \end{split}
  %  \end{equation}
%      +\beta_3Z_i+\beta_4\sti Z_i+\bm{\beta_5}'\bxy_i\sti+
 %   \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\sti+
  \end{equation}
  with $\EE[\epsilon_i]=0$ and $\{Z_i,\sti,\bxy_i\}\independent \epsilon_i$.
  Then say the following model is fit with OLS
  \begin{equation}\label{eq:fullInteractionModel}
    Y_i=\beta_0+\bm{\beta_1}'\bxy_i+\beta_2\ri+\beta_3Z_i+\beta_4\ri Z_i+\bm{\beta_5}'\bxy_i\ri+
    \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\ri+\epsilon_i
  \end{equation}
  with $\ri$ as defined in \eqref{eq:ri},
  yielding coefficient estimates $\hat{\beta}_k$, $k=0,\dots,3$.
  Then
   \begin{equation}\label{eq:prinEffEst}
  \begin{split}
    \hat{\eff0}_{int}&\equiv \hat{\beta}_3+\bm{\beta}_6'\overline{\bxy}_{Z=1,S=0}\\
    \hat{\eff1}_{int}&\equiv \hat{\beta}_3+(\bm{\hat{\beta}_6}+\bm{\hat{\beta}_7})'\overline{\bxy}_{Z=1,S=1}
  \end{split}
\end{equation}
   are M-estimators, with $\hat{\eff0}_{int}\rightarrow_p\eff0$ and $\hat{\eff1}_{int}\rightarrow_p\eff1$ as $n\rightarrow\infty$,
   where $\overline{\bxy}_{Z=1,S=s}$ is a vector of the $k$ column means of the rows of $\bxy$ corresponding to subjects with $Z=1$ and $S=s$.
\end{prop}

@@

\subsubsection{Manipulated Factors}
We manipulated five factors in the simulation:
\begin{itemize}
%\item Sample size $n\in\{500,1000\}$
\item $\muc1\in\{0,0.3\}$
\item $\alpha \in \{0,0.2,0.5,1\}$
\item The distribution of $\epsilon_i$
\item The presence of interactions between $\st$ and covariates
\item The presence of interactions between $Z$ and covariates
\end{itemize}

@@

As mentioned above, $\alpha$ controls the variance of the principal scores, i.e. the extent to which $\st$ is predictible as a function of covariates. When $\alpha=0$, the covariates are unrelated to $\st$ and principal scores do not vary between participants, violating \eqref{eq:vps}. We expect that the more predictive the covariates, the better the performance of all three estimators.

$\epsilon$ is the regression error in \eqref{eq:yc-sim}. Across simulation runs, $E[\epsilon]=0$ and $Var(\epsilon)=1/2$. However, the shape of $\epsilon$'s distribution varied between the following three possibilities:
\begin{itemize}
\item[Normal] $\epsilon~\mathcal{N}(0,1/2)$, as assumed by the mixture model estimator
\item[Uniform] $\epsilon~\mathcal{U}(-\sqrt{6}/2,\sqrt{6}/2)$
\item[Mixture] $f_\epsilon(x)=\frac{1}{4}\phi\left((x+1/3)\sqrt{6}\right)+\frac{1}{4}\phi\left((x-1)\sqrt{6})\right)$
\end{itemize}
The mixture distribution for $\epsilon$ was designed to be particularly difficult for the mixture model estimator.

@@

All three methods used the same principal score model, fit using data from the treatment group in which $S=\st$ was observed:
\begin{equation}\label{eq:psModsim}
  \fpp{\bm{\alpha}}{x_1,x_2}=logit^{-1}(\alpha_0+\alpha_1x_1+\alpha_2x_2)
\end{equation}

@@

\subsection{Results}

\begin{figure}
  \centring
  \includegraphics{../simFigs/normalOutcomesNoInteractionPosB1.jpg}
  \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} when the distribution of residuals in \eqref{eq:yc-sim} was normal, there were no interactions between covariates and $S$ or $Z$, and $\alpha=0.2,0.5$. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
  \label{fig:simNorm}
\end{figure}

\begin{figure}
  \centring
  \includegraphics{../simFigs/unifOutcomesNoInteractionPosB1.jpg}
  \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} when the distribution of residuals in \eqref{eq:yc-sim} was uniform, there were no interactions between covariates and $S$ or $Z$, and $\alpha=0.2,0.5$. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
  \label{fig:simUnif}
\end{figure}

\begin{figure}
  \centring
  \includegraphics{../simFigs/InteractionPosB1.jpg}
  \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} when the distribution of residuals in \eqref{eq:yc-sim} was normal, there were possibly interactions between covariates and $S$ or $Z$, $\muc1=0.3$, and $\alpha=0.5$. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
  \label{fig:simUnif}
\end{figure}

@@

\begin{table}
  \input{coverageTab}
  \caption{Coverage}
\end{table}

@@

\subsection{Proof for Proposition \ref{prop:interaction}}
First, note that $\EE[S]=\EE\EE[S|\bx]=\EE[\pp]$ and
$$\EE[\bx S]=\EE[\bx S|Z=1]=\EE[\bx S|Z=0]=\EE[\bx \EE[\bx\EE[S|\bx]|Z=0]]=\EE[\bx\pp|Z=0]=\EE[\bx\pp]$$
implying that
\begin{equation*}
  \begin{split}
    \EE[Y|\bx,Z=0]&=\beta_0+\bm{\beta_1}\bxy+\beta_2\pp+\bm{\beta_5}'\bxy\pp\tag*{and}\\
    \EE[Y|\bx,S,Z=1]&=\beta_0+\beta_3+(\bm{\beta_1}+\bm{\beta_6})\bxy+(\beta_3+\beta_4)S+(\bm{\beta_5}+\bm{\beta_7})'\bxy S
  \end{split}
\end{equation*}
Therefore,
\begin{align*}
  \EE[Y]&=\EE[Y|Z=0]+\EE[Z]\left\{\EE[Y|Z=1]-\EE[Y|Z=0]\right\}\\
  &=\beta_0+\bm{\beta_1}\EE[\bxy]+\beta_2\EE[\pp]+\bm{\beta_5}'\EE[\bxy\pp]+\EE[Z]\left\{\beta_3+\bm{\beta_4}\EE[S]+\bm{\beta_6}'\EE[\bxy]+\bm{\beta_7}'\EE[\bxy S]\right\}\\
  &=\beta_0+\bm{\beta_1}\EE[\bxy]+\beta_2\EE[R]+\bm{\beta_5}'\EE[\bxyR]+\EE[Z]\left\{\beta_3+\bm{\beta_4}\EE[R]+\bm{\beta_6}'\EE[\bxy]+\bm{\beta_7}'\EE[\bxy R]\right\}\\
\end{align*}
Analogous reasoning leads to expressions for $\EE[RY]$, $\EE[\bxy Y]$, $\EE[ZY]$,  $\EE[ZRY]$, $\EE[\bxy YZ]$, and $\EE[\bxy RZY]$.
These, in turn, give rise to estimating equations
\begin{equation*}

  \displaystyle\sum_i \begin{pmatrix}
    Y_i-\beta_0-\bm{\beta_1}\bxy_i-\beta_2R_i-\bm{\beta_5}'\bxy_iR_i-Z_i\left\{\beta_3-\bm{\beta_4}R_i-\bm{\beta_6}'\bxy_i-\bm{\beta_7}'\bxy_i R_i\right\}\\
    R_iY_i-\beta_0R_i-\bm{\beta_1}\bxy_iR_i-\beta_2R_i^2-\bm{\beta_5}'\bxy_iR_i^2-Z_i\left\{\beta_3R_i-\bm{\beta_4}R_i^2-\bm{\beta_6}'\bxy_iR_i-\bm{\beta_7}'\bxy_i R_i^2\right\}\\
    \bxy_i Y_i-\beta_0\bxy_i-\bm{\beta_1}\bxy_i\bxy_i'-\beta_2R_i\bxy_i-\bm{\beta_5}'\bxy_iR_i-Z_i\left\{\beta_3\bxy_i-\bm{\beta_4}R_i\bxy_i-\bm{\beta_6}'\bxy_i\bxy_i'-\bm{\beta_7}'\bxy_i\bxy_i' R_i\right\}\\
    Z_iY_i-Z_i\left\{\beta_0-\bm{\beta_1}\bxy_i-\beta_2R_i-\bm{\beta_5}'\bxy_iR_i-\beta_3-\bm{\beta_4}R_i-\bm{\beta_6}'\bxy_i-\bm{\beta_7}'\bxy_i R_i\right\}\\
    Z_iR_iY_i-Z_iR_i\left\{\beta_0-\bm{\beta_1}\bxy_i-\beta_2R_i-\bm{\beta_5}'\bxy_iR_i-\beta_3-\bm{\beta_4}R_i-\bm{\beta_6}'\bxy_i-\bm{\beta_7}'\bxy_i R_i\right\}\\
    Z_iY_i\bxy_i-Z_i\left\{\beta_0\bxy_i-\bm{\beta_1}\bxy_i\bxy_i'-\beta_2R_i\bxy_i-\bm{\beta_5}'\bxy_i\bxy_i'R_i-\beta_3\bxy_i-\bm{\beta_4}R_i\bxy_i-\bm{\beta_6}'\bxy_i\bxy_i'-\bm{\beta_7}'\bxy_i\bxy_i' R_i\right\}\\
    R_iZ_iY_i\bxy_i-Z_iR_i\left\{\beta_0\bxy_i-\bm{\beta_1}\bxy_i\bxy_i'-\beta_2R_i\bxy_i-\bm{\beta_5}'\bxy_i\bxy_i'R_i-\beta_3\bxy_i-\bm{\beta_4}R_i\bxy_i-\bm{\beta_6}'\bxy_i\bxy_i'-\bm{\beta_7}'\bxy_i\bxy_i' R_i\right\}
  \end{pmatrix}=\begin{pmatrix} 0\\0\\0\\0\\0\\0\\0\end{pmatrix}
\end{equation*}
These are the estimating equations for the regression model \eqref{eq:fullInteractionModel}, fit by OLS. Now note that
\begin{equation*}
  \EE[Y_T-Y_C|\st=0]=\beta_0^T-\beta_0^C+(\bm{\beta_1}^T'-\bm{\beta_1}^C')\EE[\xby|S=0]=\beta_3+\beta_6'E[\xby|S=0]
\end{equation*}
and
\begin{equation*}
  \EE[Y_T-Y_C|\st=1]=\beta_0^T+\beta_2^T-(\beta_0^C+\beta_2^C)+(\bm{\beta_1}^T'+\bm{\beta_3^T}'-\bm{\beta_1}^C'-\bm{\beta_3^C}')\EE[\xby|S=0]=\beta_3+\beta_4+(\beta_6'+\beta_7')E[\xby|S=1]
\end{equation*}
the result follows

>>>>

\subsection{Relaxing Covariate Ignorability}
In most applications, identifying a set of covariates $\bxs$ satisfying CI will be difficult or impossible.
Fortunately, CI may be relaxed or obviated by regression.
Let $\bxy\in \mathbb{R}^k$, be a vector of covariates (possibly the same as $\bxs$); $\bxy$ can contain transformations and interactions of baseline covariates, allowing for a wide range of models.
Then note that $\st$ is, essentially, a covariate, so by randomization, (Assumption \ref{ass:rand}), $\EE[\bxy|\st]=\EE[\bxy|\st,Z=0]=\EE[\bxy|\st,Z=1]$.
Then information about the stratum-specific means of $\bxy$ can be extrapolated from the treatment to the control group.
This leads to the following proposition:
\begin{prop}\label{prop:interactions}
  Say
  \begin{equation}\label{eq:interaction}
    \begin{split}
      Y_{Ci}=\beta_0^C+\bm{\beta_1}^{C'}\bxy_i+\beta_2^C\sti+\bm{\beta_3^{C'}}\bxy_i\sti+\epsilon_{Ci}\\
      Y_{Ti}=\beta_0^T+\bm{\beta_1}^{T'}\bxy_i+\beta_2^T\sti+\bm{\beta_3^{T'}}\bxy_i\sti+\epsilon_{Ti}\\
    \end{split}
  %  \end{equation}
%      +\beta_3Z_i+\beta_4\sti Z_i+\bm{\beta_5}'\bxy_i\sti+
 %   \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\sti+
  \end{equation}
  with $\EE[\epsilon_i]=0$ and $\{Z_i,\sti,\bxy_i\}\independent \epsilon_i$.
  Then say the following model is fit with OLS
  \begin{equation}\label{eq:fullInteractionModel}
    Y_i=\beta_0+\bm{\beta_1}'\bxy_i+\beta_2\ri+\beta_3Z_i+\beta_4\ri Z_i+\bm{\beta_5}'\bxy_i\ri+
    \bm{\beta_6}'\bxy Z_i+\bm{\beta_7}'\bxy_i Z_i\ri+\epsilon_i
  \end{equation}
  with $\ri$ as defined in \eqref{eq:ri},
  yielding coefficient estimates $\hat{\beta}_k$, $k=0,\dots,3$.
  Then
   \begin{equation}\label{eq:prinEffEst}
  \begin{split}
    \hat{\eff0}_{int}&\equiv \hat{\beta}_3+\bm{\beta}_6'\overline{\bxy}_{Z=1,S=0}\\
    \hat{\eff1}_{int}&\equiv \hat{\beta}_3+(\bm{\hat{\beta}_6}+\bm{\hat{\beta}_7})'\overline{\bxy}_{Z=1,S=1}
  \end{split}
\end{equation}
   are M-estimators, with $\hat{\eff0}_{int}\rightarrow_p\eff0$ and $\hat{\eff1}_{int}\rightarrow_p\eff1$ as $n\rightarrow\infty$,
   where $\overline{\bxy}_{Z=1,S=s}$ is a vector of the $k$ column means of the rows of $\bxy$ corresponding to subjects with $Z=1$ and $S=s$.
\end{prop}

@@

\subsubsection{Manipulated Factors}
We manipulated six factors in the simulation:
\begin{itemize}
\item Sample size per treatment group $n\in\{100,200,\dots,1000\}$
\item $\alpha \in \{0,0.2,0.3,\dots,1\}$
\item $\muc1\in\{0,0.3\}$
\item The distribution of $\epsilon_i$
\item The presence of interactions between $\st$ and covariates
\item The presence of interactions between $Z$ and covariates
\end{itemize}
The six factors are not completely crossed---in particular, we let $n$ and $\alpha$ each vary across all the levels listed while holding the other five factors fixed.

The guarentees of M-estimation are all assymptotic, so we examined the behavior of our M-estimator at a range of sample sizes to determine its finite-sample properties.

@@

As mentioned above, $\alpha$ controls the variance of the principal scores, i.e. the extent to which $\st$ is predictible as a function of covariates. When $\alpha=0$, the covariates are unrelated to $\st$ and principal scores do not vary between participants, violating \eqref{eq:vps}. We expect that the more predictive the covariates, the better the performance of all three estimators.
To aid in the interpretation of the $\alpha$ parameter, the online appendix plots $\alpha$ against the area under the receiver operating characteristic curve for each fitted model (AUC), a common measure of classification accuracy \citep{bradley1997use}---an AUC of 0.5 implies that the model is no better than random guessing, and AUC of 1 implieds perfect prediction. For $0.5\le \alpha \le 1$, the average AUC varies from roughly 0.53 to 0.77; for $\alpha=0.5$, the average AUC was roughly 0.675.

$\epsilon$ is the regression error in \eqref{eq:yc-sim}. Across simulation runs, $E[\epsilon]=0$ and $Var(\epsilon)=1/2$. However, the shape of $\epsilon$'s distribution varied between the following two possibilities:
\begin{itemize}
\item[Normal] $\epsilon\sim\mathcal{N}(0,1/2)$, as assumed by the mixture model estimator
\item[Uniform] $\epsilon\sim\mathcal{U}(-\sqrt{6}/2,\sqrt{6}/2)$
%\item[Mixture] $f_\epsilon(x)=\frac{1}{4}\phi\left((x+1/3)\sqrt{6}\right)+\frac{1}{4}\phi\left((x-1)\sqrt{6})\right)$
\end{itemize}
%The mixture distribution for $\epsilon$ was designed to be particularly difficult for the mixture model estimator.

@@

All three methods used the same principal score model, fit using data from the treatment group in which $S=\st$ was observed:
\begin{equation}\label{eq:psModsim}
  \ppf{\bm{\alpha}}{x_1,x_2}=logit^{-1}(\alpha_0+\alpha_1x_1+\alpha_2x_2)
\end{equation}

@@

\subsection{Results}
In this section we present the subset of simulation results that we think is the most telling and interesting; a fuller set of results is available in the online appendix.

\subsubsection{Varying $n$ and $\alpha$}
When $\alpha=0$, Assumption \ref{ass:vps} is violated, and M-estimates are highly erratic; however, as Table \ref{tab:coverage} shows, when other assumptions hold inference remains valid.
For the sake of clarity, we will focus here on cases where $\alpha>0$; results for $\alpha=0$ are in Tables \ref{tab:rmse} and \ref{tab:coverage} and in the online appendix.

Figures \ref{fig:n} and \ref{fig:alpha} show the empirical bias and standard error (SE) of the M-estimator and mixture estimator of $\eff1$ as sample size and $\alpha$ vary.
Across $n$ and $\alpha$, the M-estimator has lower bias and higher SE than the mixture estimator.
The M-estimator is positively biased for low $n$ with bias converging to close to 0 (up to simulation error) for $n\ge 300$, and appears to be roughly unbiased (up to simulation error) for $0.2\le \alpha 1$, with $n$ fixed at 500.
The SE of the M-estimator decreases rapidly for $100\le n \le 500$ and $0.2\le \alpha \le 0.5$ and more gradually for higher values of $n$ and $\alpha$.

For the remainder of the simulation, we focus on the moderate cases of $n=500$ and $\alpha=0.2$ or 0.5.

\begin{figure}
  \centering
  \includegraphics{../simFigs/biasSEbyN.jpg}
  \caption{Empirical bias and standard error of M- and Mixture estimates of $\muc1$ as sample size per treatment group $n$ varies from 0 to 1. There were 500 replications for each $n$. Other factors were held fixed at the noted values.}
  \label{fig:n}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{../simFigs/biasSEbyB1.jpg}
  \caption{Empirical bias and standard error of M- and Mixture estimates of $\muc1$ as $\alpha$ varies from 0.1 to 1. There were 500 replications for each $n$. Other factors were held fixed at the noted values.}
  \label{fig:alpha}
\end{figure}

\subsubsection{Other Factors}

\begin{figure}
  \centering
  \includegraphics{../simFigs/boxplots.pdf}
  \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} under varying conditions. For all plots, $n=500$; there were 500 replications for each set of conditions. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
  \label{fig:boxplots}
\end{figure}

Figure \ref{fig:boxplots} shows violin plots, layered on top of jitters scatterplots, showing estimation error for the M-estimator, the mixture estimator, and the PSW estimator of $\eff1$ under various sets of conditions, and Table \ref{tab:rmse} shows root mean squared error (RMSE) estimates under a somewhat wider set of circumstances when $\muc1=0.3$.
The leftmost panel of Figure \ref{fig:boxplots} and the top line of Table \ref{tab:rmse} show results under ``standard'' conditions---normal residuals and no interactions in the data generating model between covariates and either $S$ or $Z$.
In this case, the M-estimator is roughly unbiased, but less precise than the other two methods---when $\alpha=0.2$ it is much noisier, and when $\alpha=0.5$ it is only slightly less precise.
The mixture estimator's bias depends on $\muc1$---when $\muc1=0$, the bias is slight, and when $\muc1=0.3$ the bias is more substantial. This is somewhat surprising, because when $\muc1=0$, there is no separation (``dispersion'') between the principal strata in the control group, and previous literature \citep{griffin2008application} has identified this scenario as a particular challenge for mixture modeling.
The PSW estimator is also biased---due, presumeably, to the violation of Principal Ignorability, Assumption \ref{ass:pi}--inherent in the data generating model. On the other hand, the PSW estimator has easily the lowest sampling variance of the three estimators.
In fact, Table \ref{tab:rmse} shows that despite its bias, the PSW estimator has lower RMSE than the M-estimator when $\alpha=0$ or 0.2.
The middle panel of Figure \ref{fig:boxplots} and the fifth line of Table \ref{tab:rmse} shows a similar set of results for when the residuals in \eqref{eq:yc-sim} are uniformly distributed.
In this case, the M-estimator and PSW estimator behave in a similiar fashion to the normal case, but the mixture estimator shows a bimodal pattern--sometimes over-estimating $\eff0$ and sometimes underestimating, but rarely estimationg $\eff1$ accurately.

The rightmost panel of Figure \ref{fig:boxplots} returns to the case of normal residuals---and only shows results when $\muc1=0.3$ and $\alpha=0.5$---but introduces interactions in the data generating model between covariates and either $\st$, $Z$, or both. That is, the coefficients on the covariates in the outcome model vary between principal strata and/or between treatment groups.
Corresponding RMSE results, along with analogous results for uniform residuals and other values for $\alpha$, are in Table \ref{tab:rmse}.
Presence of interactions could undermine the M-estimate by inducing a relationship between principal scores and potential outcomes, even after adjusting the outcomes for covariate effects.
Fortunately, the presence of interactions in the data generating model in this scenario appear to make little difference, though RMSEs were slightly higher when interactions between $Z$ and covariates are present.
Table \ref{tab:rmse} shows that when $\alpha=.2$, M-estimation RMSE can be substantially higher when $Z$ interactions are present than when they are not; plots in the online appendix suggest that this is due to an increase in sampling variance and kurtosis rather than bias.

Table \ref{tab:coverate} shows estimates of the empirical coverage of nominal 95\% confidence intervals for the M-estimator and mixture estimator of $\eff1$, to evaluate their respective standard error estimates and the associated statistical inference.
When $\alpha=0.5$, M-estimator confidence intervals consistently acheive their nominal levels\footnote{With 500 replications and true coverage probabilities of 0.95, the standard error for emperical coverage rates is approximately 1 percentage point.}, whereas confidence intervals from mixture estimators undercover in the presence of interactions between $Z$ and $X$, or when residuals are non-normal.
When $\alpha=0$ or 0.2, M-estimation confidence intervals undercover in the presence of interactions between $X$ and $Z$.
Across all conditions in the table, the M-estimation confidence intervals have higher empirical coverage than their mixture-model counterparts.

%% \begin{figure}
%%   \centring
%%   \includegraphics{../simFigs/normalOutcomesNoInteractionPosB1.jpg}
%%   \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} when the distribution of residuals in \eqref{eq:yc-sim} was normal, there were no interactions between covariates and $S$ or $Z$, and $\alpha=0.2,0.5$. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
%%   \label{fig:simNorm}
%% \end{figure}

%% \begin{figure}
%%   \centring
%%   \includegraphics{../simFigs/unifOutcomesNoInteractionPosB1.jpg}
%%   \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} when the distribution of residuals in \eqref{eq:yc-sim} was uniform, there were no interactions between covariates and $S$ or $Z$, and $\alpha=0.2,0.5$. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
%%   \label{fig:simUnif}
%% \end{figure}

%% \begin{figure}
%%   \centring
%%   \includegraphics{../simFigs/InteractionPosB1.jpg}
%%   \caption{Violin and scatterplots of 500 simulation estimation errors for estimators described in Section~\ref{sec:simMods} when the distribution of residuals in \eqref{eq:yc-sim} was normal, there were possibly interactions between covariates and $S$ or $Z$, $\muc1=0.3$, and $\alpha=0.5$. Annotations at the upper and lower edges of the plot indicate the number of extreme outliers excluded from the plotting area.}
%%   \label{fig:simUnif}
%% \end{figure}

@@

\begin{table}
  \input{coverageTab}
  \caption{Coverage}
  \label{tab:coverage}
\end{table}

@@

\subsection{Proof for Proposition \ref{prop:interaction}}
First, note that $\EE[S]=\EE\EE[S|\bx]=\EE[\pp]$ and
$$\EE[\bx S]=\EE[\bx S|Z=1]=\EE[\bx S|Z=0]=\EE[\bx \EE[\bx\EE[S|\bx]|Z=0]]=\EE[\bx\pp|Z=0]=\EE[\bx\pp]$$
implying that
\begin{equation*}
  \begin{split}
    \EE[Y|\bx,Z=0]&=\beta_0+\bm{\beta_1}\bxy+\beta_2\pp+\bm{\beta_5}'\bxy\pp\\
    \EE[Y|\bx,S,Z=1]&=\beta_0+\beta_3+(\bm{\beta_1}+\bm{\beta_6})\bxy+(\beta_3+\beta_4)S+(\bm{\beta_5}+\bm{\beta_7})'\bxy S
  \end{split}
\end{equation*}
Therefore,
\begin{align*}
  \EE[Y]&=\EE[Y|Z=0]+\EE[Z]\left\{\EE[Y|Z=1]-\EE[Y|Z=0]\right\}\\
  &=\beta_0+\bm{\beta_1}\EE[\bxy]+\beta_2\EE[\pp]+\bm{\beta_5}'\EE[\bxy\pp]+\EE[Z]\left\{\beta_3+\bm{\beta_4}\EE[S]+\bm{\beta_6}'\EE[\bxy]+\bm{\beta_7}'\EE[\bxy S]\right\}\\
  &=\beta_0+\bm{\beta_1}\EE[\bxy]+\beta_2\EE[R]+\bm{\beta_5}'\EE[\bxy R]+\EE[Z]\left\{\beta_3+\bm{\beta_4}\EE[R]+\bm{\beta_6}'\EE[\bxy]+\bm{\beta_7}'\EE[\bxy R]\right\}\\
\end{align*}
Analogous reasoning leads to expressions for $\EE[RY]$, $\EE[\bxy Y]$, $\EE[ZY]$,  $\EE[ZRY]$, $\EE[\bxy YZ]$, and $\EE[\bxy RZY]$.
These, in turn, give rise to estimating equations
\begin{equation*}
  \displaystyle\sum_i \begin{pmatrix}
    Y_i-\beta_0-\bm{\beta_1}\bxy_i-\beta_2R_i-\bm{\beta_5}'\bxy_iR_i-Z_i\left\{\beta_3-\bm{\beta_4}R_i-\bm{\beta_6}'\bxy_i-\bm{\beta_7}'\bxy_i R_i\right\}\\
    R_iY_i-\beta_0R_i-\bm{\beta_1}\bxy_i R_i-\beta_2R_i^2-\bm{\beta_5}'\bxy_iR_i^2-Z_i\left\{\beta_3R_i-\bm{\beta_4}R_i^2-\bm{\beta_6}'\bxy_iR_i-\bm{\beta_7}'\bxy_i R_i^2\right\}\\
    \bxy_i Y_i-\beta_0\bxy_i-\bm{\beta_1}\bxy_i\bx^{Y'}_i-\beta_2R_i\bxy_i-\bm{\beta_5}'\bxy_iR_i-Z_i\left\{\beta_3\bxy_i-\bm{\beta_4}R_i\bxy_i-\bm{\beta_6}'\bxy_i\bx^{Y'}_i-\bm{\beta_7}'\bxy_i\bx^{Y'}_i R_i\right\}\\
    Z_iY_i-Z_i\left\{\beta_0-\bm{\beta_1}\bxy_i-\beta_2R_i-\bm{\beta_5}'\bxy_iR_i-\beta_3-\bm{\beta_4}R_i-\bm{\beta_6}'\bxy_i-\bm{\beta_7}'\bxy_i R_i\right\}\\
    Z_iR_iY_i-Z_iR_i\left\{\beta_0-\bm{\beta_1}\bxy_i-\beta_2R_i-\bm{\beta_5}'\bxy_iR_i-\beta_3-\bm{\beta_4}R_i-\bm{\beta_6}'\bxy_i-\bm{\beta_7}'\bxy_i R_i\right\}\\
    Z_iY_i\bxy_i-Z_i\left\{\beta_0\bxy_i-\bm{\beta_1}\bxy_i\bx^{Y'}_i-\beta_2R_i\bxy_i-\bm{\beta_5}'\bxy_i\bx^{Y'}_iR_i-\beta_3\bxy_i-\bm{\beta_4}R_i\bxy_i-\bm{\beta_6}'\bxy_i\bx^{Y'}_i-\bm{\beta_7}'\bxy_i\bx^{Y'}_i R_i\right\}\\
    R_iZ_iY_i\bxy_i-Z_iR_i\left\{\beta_0\bxy_i-\bm{\beta_1}\bxy_i\bx^{Y'}_i-\beta_2R_i\bxy_i-\bm{\beta_5}'\bxy_i\bx^{Y'}_iR_i-\beta_3\bxy_i-\bm{\beta_4}R_i\bxy_i-\bm{\beta_6}'\bxy_i\bx^{Y'}_i-\bm{\beta_7}'\bxy_i\bx^{Y'}_i R_i\right\}
  \end{pmatrix}=\begin{pmatrix} 0\\0\\0\\0\\0\\0\\0\end{pmatrix}
\end{equation*}
These are the estimating equations for the regression model \eqref{eq:fullInteractionModel}, fit by OLS. Now note that
\begin{equation*}
  \EE[Y_T-Y_C|\st=0]=\beta_0^T-\beta_0^C+(\bm{\beta_1}^{T'}-\bm{\beta_1}^{C'})\EE[\bxy|S=0]=\beta_3+\beta_6'E[\bxy|S=0]
\end{equation*}
and
\begin{equation*}
  \EE[Y_T-Y_C|\st=1]=\beta_0^T+\beta_2^T-(\beta_0^C+\beta_2^C)+(\bm{\beta_1}^{T'}+\bm{\beta_3^{Ti}}-\bm{\beta_1}^{C'}-\bm{\beta_3^{C'}})\EE[\bxy|S=0]=\beta_3+\beta_4+(\beta_6'+\beta_7')E[\bxy|S=1]
\end{equation*}
the result follows
